Jeff Goldsmith

### 2018-06-03 index.Rmd
minor updates

<link rel="stylesheet" href="styles.css" type="text/css">

### Assistant Professor of Biostatistics, Columbia University Mailman School of Public Health

<br><img src="images/jeff.jpg" alt="jeff" style="width:85%; border:10px solid"><br>

@@

#### Curriculum Vitae

My full CV is availble [here](Downloads/CV_Goldsmith.pdf).

>>>>

<link rel="stylesheet" href="styles.css" type="text/css">
<link rel="stylesheet" href="academicons/css/academicons.min.css"/>

Associate Professor of Biostatistics <br>
Columbia University Mailman School of Public Health

<br><img src="images/jeff.jpg" alt="jeff" style="width:65%; border:10px solid"><br>

#### About

@@
